---
title: "Query Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Query Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(koadata) 
```

The query functions are used to search the database directly and pull information from multiple tables at once. 

All query functions by default will provide the following information:

* CAS No. of the chemical
* Chemical Name (as listed in the database)
* Temperature (°C) of the *K*~OA~ value
* log~10~ *K*~OA~ value
* Method's score (0 to 4)
* Experimental or estimated value (EXP or EST)
* Method bin (QSPR, Solvation, RT, etc.)
* Citation
* Note on reliability
* Comments during data curation

## more.info Argument

If the more.info argument is specified as TRUE, then additional columns information is also extracted from the database:

* Chemical category
* All chemical names/synonyms and acronyms included in the database
* Molar mass of the chemical
* Type of method ("Dynamic", "Static", "Indirect", "EST")
* Specificity regarding the method (UPPER, COSMOtherm, SR-GC-RT, etc.)
* Type of octanol (wet or dry)
* Way the *K*~OA~ was original reported in the reference
* Reference Group

By default the more.info argument is FALSE.

## Query by CAS No.

The `query.cas()` function can be used to extract *K*~OA~ information regarding a specific chemical with a known CAS No. The CAS No. does not need to include hyphens (-).

```{r}
# query.cas("87-82-1")
 
# query.cas("87821", more.info = T)
```

## Query by Name

Using the `query.name()` function extracts *K*~OA~ information where the query matches a chemical name within the database. This search matches the names exactly to what is within the database. Only the common name as included in the database will be in the output. To include include all names from the databse in the output, `more.info` must be TRUE (default is FALSE).

```{r}

# query.name("PCB-82") #The name does not match what is in the database.

# query.name("PCB 82")

# query.name("PCB 82", more.info = T)
 
# query.name("o,p'-DDD")
 
# query.name("3-Methylbutan-2-one")
```

## Query by Category

*K*~OA~ data from all chemicals within a specific category can be extracted using the `query.category()` function. To see chemical categories in the output, ensure `more.info = T`. See `get.categories()` to obtain a list of query options.

```{r}
#query.category("HCH")

#query.mass(350, 400, more.info = T)
```


## Query by Mass

The database can be queried to find *K*~OA~ data for chemicals with a specific molar mass or within a range of molar masses using `query.mass()`. By default the molar mass is not included in the output, specifying `more.info` as `TRUE` will include the molar mass in the output.

```{r}
#query.mass(350, 400)

#query.mass(350, 400, more.info = T)
```

To query a specific mass, specify the mass as both the upper and lower limit.

``` {r}
#query.mass(106.168, 106.168)
```

## Query by Citation

To pull all *K*~OA~ data from a specific citation or reference you can use the `query.citation()` function. The queries must be exact matches to what is included in the database. To obtain a list of citations in the database, use the `get.citations()` function.

```{r}
#query.citation("Meylan and Howard 2005")
```


## Query by Group

The `query.group()` functions allows you to obtain all data from a specific research group. The function below will pull all *K*~OA~ data from the work by the Carr group.

```{r}
# query.group("Carr")
```


##Query by Method

There are two functions that allow you to search the database by methods. The `query.meth.type()` function will extract all *K*~OA~ data from "Dynamic", "Static", Indirect", or "EST" methods. 

```{r}
#query.meth.type("Static")
```

The `query.meth()` function is more specific and searches for specific experimental and estimated methods: "FM", "QSPR", "Dy-GLC-RT", "HS", "RT", "droplet", "Eqbm", "Solvation", "VP", "GasSol", or "GS". 

```{r}
#query.meth("Solvation")
#query.meth("droplet")
```

## Multiple/batch Queries

Except for the query.mass function, the functions allow for multiple search parameters. Simply include all search terms as a list within the query argument.

```{r}
# query.cas(c("105-54-4", "319-85-7"))

# query.name(c("Dibromobisphenol A", "Barbital"))

# query.category(c("CDD", "CDF"))

# query.citation(c("Parnis et al. 2015", "Finizio et al. 1997"))

# query.group(c("Bidleman", "Chen"))
```

